\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}
This thesis is a joint work between \acrfull{uio}, \acrfull{simulamet} and \acrfull{oslomet}. First and foremost I would like to thank my supervisors Hugo L. Hammer (\acrshort{oslomet}) and Michael Riegler (\acrshort{simulamet}) for suggesting this interesting topic of \textit{Applying artificial intelligence to perform climate predictions}, and to Trude Storelvmo (\acrshort{uio}) for joining us, allowing me to shift the focus toward applications to cloudphysics.

It is a poor workman who blames his tools, I admire how you tackled the corona pandemic and lead me safely to shore. Thanks for your patience, kindness and fruitful discussions, I've learned a lot from working with you!

I would also like to thank the scientist at EUMETSAT. 
Their expertise have been invaluable when generating the dataset. 
Hans Petter Verne in IT-support on the GEO-department for your technical support regarding storage space among other things has been greatly appreciated.

I would also like to thank Raymond Wiker, Jonah Shaw and Ina Storteig for their support and insightful comments. Your contribution have been valuable for my work.

A big thanks goes to my fellow master students, friends and family. \textbf{Ny setning, Your support have been great}. Finally, the constant encouragement of my sister, Sara, is sincerely appreciated.
%A big thanks goes to my sister Sara for her unconditional support and for occasionally keeping me company as MetOs. Its much appreciated. 
%Thanks to Michael Schulz and Jan Griesfeller for giving me access to Modis6.1 Terra data, prepossessing the data. 
%Kind and patient supervisors for listening to \textit{all my great ideas}.
\cleardoublepage